\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-30 manuscript.Rmd

<!-- - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]` -->
<!-- - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]` -->
<!-- - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]` -->
<!-- - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]` -->
<!-- - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]` -->
<!-- - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]` -->
<!-- - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]` -->
<!-- - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]` -->
<!-- - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]` -->
<!-- - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]` -->

>>>>

- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
